Test if analytic derivation of geodesic distance for curves from sim_functional_data.R

### 2019-05-16 test_analytic_geodesic_distance.Rmd
html update
added abstract/title from IMS china writeup. took out caching in test_analytic_geodesic_distance markdown

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

@@

```{r}
library(reticulate)
# sometimes reticulate requires specific instruction on where to find your python
# first call Sys.which("python") and then copy that path into 
#use_python('/Users/suswei/anaconda3/bin/python',required=TRUE)
use_python('/anaconda3/bin/python',required=TRUE)
get_min_num_neighbors = import_from_path("get_min_num_neighbors",path='.')
getIsomapGdist = import_from_path("getIsomapGdist",path='.')

>>>>

# ```{r setup, include=FALSE}
# #knitr::opts_chunk$set(cache = TRUE)
# ```

@@

```{r}
library(reticulate)
# sometimes reticulate requires specific instruction on where to find your python
# first call Sys.which("python") and then copy that path into 
use_python('/Users/suswei/anaconda3/bin/python',required=TRUE)
#use_python('/anaconda3/bin/python',required=TRUE)
get_min_num_neighbors = import_from_path("get_min_num_neighbors",path='.')
getIsomapGdist = import_from_path("getIsomapGdist",path='.')
